### 2018-09-11 pilot_manuscript.Rmd
updated sage and thesis stuff

```{r new_data, include = FALSE}

@@

@@

@@

>>>>

```{r new_data, include = FALSE}
##open the Warriner data for later
warriner = read.csv("BRM-emot-submit.csv", stringsAsFactors = F) #want v.mean.sum

for(i in 1:nrow(warriner)) {
  warriner$Word2[i] = stemDocument(warriner$Word[i], language = "english")
}

@@

#control here for times when no words
if (nrow(temp2) == 0){
  temp2 = data.frame("Var1" = 0, "Freq" = 0)
}

@@

#pull in the data from Warriner 
library(expss)
harm_final_data$valence = vlookup(harm_final_data$Var1, #index in original data
                                  warriner, #where's the stuff you want to put in
                                  "V.Mean.Sum", #what column is the stuff you want
                                  "Word2") #what's the matching index

#figure out stupid words
#table(harm_final_data$Var1[is.na(harm_final_data$valence) & harm_final_data$Freq > 0])
#fought, safer, spurn

@@

```{r descriptives, include = FALSE}
#summarize the dataset so that you have the total and percent for each foundation

#report descriptive statistics of the foundations

#note that a big problem is the valence of the words 
```
